---
title: "Sourcing and Importing Data"
subtitle: "Introduction to Text as Data"
author: "Amber Boydstun & Cory Struthers"
date: "April 27-29, 2023"
output:
  html_document:
    toc: yes
    df_print: paged
  html_notebook:
    code_folding: show
    highlight: tango
    theme: united
    toc: yes
    df_print: paged
---


```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = "~/Dropbox/text-as-data-JUST-CORY-AND-AMBER/modules/data/")
```

### Introduction

Text data come from myriad sources. Organizing and loading the text data is the first step to familiarizing ourselves with the data to analyze. In this module, we will cover some (but not all) of the ways available for organizing text data.

In this module, we'll need the following packages:

``` {r, results = 'hide', message = FALSE}

# Load packages
require(tidyverse)
require(readxl)
require(writexl)
require(quanteda)
require(readtext)

# Set working directory
setwd("/Users/cs86487/Dropbox/text-as-data-JUST-CORY-AND-AMBER/modules/data/")
getwd() # view working directory

```

\

###  Load text data from different sources

Sometimes text data comes to us neatly, where a column in an excel or csv file includes texts and columns in the same data file provide information about each text. In these cases, we can use base R or R packages design to upload traditional types of data, like `readxl`.

Below, we load data we use several times in the course and add a variable `doc_id_keep`, which will come in handy later in the course.

```{r, message = FALSE}

# Readxl for xlsx file
news_data = read_xlsx("sample_news_1995-2017.xlsx") %>%
    mutate(doc_id_keep  = paste0("text",row_number()))

# Base R for CSV file
tweet_data = read.csv("sample_immigration_tweets_2013-2017.csv") %>%
    mutate(doc_id_keep  = paste0("text",row_number()))

# Base for RDS file (R object)
bills_data = readRDS("sample_bills.rds") %>%
    mutate(doc_id_keep  = paste0("text",row_number()))

```

The `readtext` package is designed to (you guessed it!) _read text_. `readtext` can handle character (txt) data in tab- or comma-seperated formats, as well as pdfs and word documents.
 
```{r, message = FALSE}

# pdf
transcript_pdf = readtext("transcript_Arizona 1.29.2020.pdf")
transcript_pdf$text

# word
transcript_word = readtext("transcript_Arizona 1.29.2020.docx")
transcript_word$text


```

More often, we need to read in multiple (sometimes hundreds of) documents from a single folder. One folder in our data folder includes several documents of committee testimony across six states. Documents don't have built-in metadata. We either have to use filenames to extract metadata or gather additional data to attach to documents as attributes. Note, this is why creating consistent, informative file names for documents is useful! 

`readtext` allows you to load multiple documents at the same time, each creating a different row in a dataframe. As shown below, the package provides options to convert text in the filenames to document variables. In the example, we use the state and dates in the names -- seperated by a space -- to create two document variables (state, date).

If you're having trouble with importing certain characters, or are being thrown an error involving Unicode, you may need to specify which encoding you want R to use in the `readtext` function, `encoding` option. Some encodings either do not import correctly or not available in R, but the problem is usually resolvable. Windows users often need to specify the encoding to prevent errors.

```{r, message = FALSE}

# Establish directory to prevent path problems
dir = "~/Dropbox/text-as-data-JUST-CORY-AND-AMBER/modules/data/transcripts"

# View files
list.files(dir) # Note excel file

# Create df of all transcripts, using filenames as document variables (metadata)
transcripts_all = readtext(paste0(dir, "/*.docx"), text_field = "texts",
                    docvarsfrom = "filenames", 
                    docvarnames = c("state", "date"),
                    dvsep = " ",
                    encoding = "ISO-8859-1") # specify encoding

# Check it out
str(transcripts_all)
names(transcripts_all)

```

\

###  Merge metadata with text documents

The transcript text may not have all variables we need to conduct analysis. We can add a metadata file with additional information to characterize the texts using standard `merge` procedures in R.

```{r, message = FALSE}

# Load metadata
transcript_metadata = read_xlsx("transcripts/Committee_testimony_metadata.xlsx")
head(transcript_metadata,10)

# Merge
transcripts_all = merge(transcripts_all, transcript_metadata, by=c("state", "date"))
head(transcripts_all,10)

```

\
<center>
**QUESTION 1: Review some of the text in the transcripts_all dataframe. What do you notice about the text records? How might the metadata mischaracterize the text records?**
</center>
\

Finally, we'll save our data with the new doc_id column.

```{r, message = FALSE}

# Save
write_xlsx(news_data, "sample_news_1995-2017_docid.xlsx", col_names = TRUE)

# Base R for CSV file
write.csv(tweet_data, "sample_immigration_tweets_2013-2017_docid.csv")

# Base for RDS file (R object)
saveRDS(bills_data, "sample_bills_docid.rds")

```

\
<center>
**QUESTION 2: Create a dataframe using the sample of legislative bills in the 'bills' folder. Upload and attach the metadata in that folder. Save as a csv file.**
</center>
\


